---
title: "visualize_model"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{visualize_model}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(mrktmix)
library(dplyr)
```

# Overview

Visualize model flags (pvalue, sign and vif) using Venn diagram

## Generating Sample Data
Here, pvalue_flag, sign_flag, and vif_flag represent logical vectors indicating the presence (TRUE) or absence (FALSE) of p-value flags, sign flags, and VIF (Variance Inflation Factor) flags, respectively. Each flag combination of flag represent one model.
```{r}
# Generate sample data for model flags
pvalue_flag <- sample(c(TRUE, FALSE), 100, replace = TRUE)
sign_flag <- sample(c(TRUE, FALSE), 100, replace = TRUE)
vif_flag <- sample(c(TRUE, FALSE), 100, replace = TRUE)
data.frame(pvalue_flag,sign_flag,vif_flag) %>%
  head()
```

## Generating Venn diagram
This function takes three arguments: pvalue_flag, sign_flag, and vif_flag, which are the logical vectors representing the model flags. The function then generates a Venn diagram plot summarizing the overlap between these flags.
```{r, out.width='100%'}
generate_model_flags_plot(pvalue_flag, sign_flag, vif_flag)
```

## Generating Sample Data
The provided R code generates sample data for analysis. It creates a data frame named contri_df with columns adstock and power, ranging from 0.1 to 0.9 in increments of 0.1. The data frame is then expanded to 1000 rows by replicating the initial data. A new column contri_perc is added, representing contribution percentages centered around 100 with variability. Finally, the first few rows of contri_df are displayed. This sample data can be used for testing and demonstration purposes.
```{r} 
# Generate dummy data
adstock_values <- seq(0.3, 0.5, by = 0.1)
power_values <- seq(0.6, 0.8, by = 0.1)
contri_df <- expand.grid(adstock = adstock_values, power = power_values)
# Increase rows to 1000
contri_df <- bind_rows(replicate(10, contri_df, simplify = FALSE))
# Add contribution percentages around 100 with some variability
contri_df$contri_perc <- rnorm(90, mean = 100, sd = 20)
contri_df %>%
  head()
```

## Plot distribution of contribution
The provided R code generates a plot illustrating the distribution of contribution percentages. It utilizes the plot_contri_dist function, passing three numeric vectors (adstock, power, and contri_perc) as input. This function generates a histogram visualizing the distribution of contribution percentages across different levels of adstock and power. The resulting plot offers insights into the distribution patterns of contribution percentages within the dataset.
```{r, out.width='100%'}
# Plot the contribution percentage distribution
plot_contri_dist(contri_df$adstock, contri_df$power, contri_df$contri_perc)
```
